Msc Thesis Figures

### 2020-08-21 ReadMe.rmd
update many

This repository contains all the code and some of the data that is needed to reproduce the work of my MSc Thesis titled:

@@

```{}
docker run -it -u rstudio -e DISABLE_AUTH=true vlucet/land_con_monteregie:3.6.2-1 \
  /bin/bash && cd ~/land_con_monteregie
```

  - **Run docker image with rstudio in your browser** (see [this post](https://ropenscilabs.github.io/r-docker-tutorial/02-Launching-Docker.html) for another example). Here you run the container in a detached mode (`-d`) on a local port (`-p 8787:8787`). Then, go to `http://192.168.99.100:8787` in your browser to access Rstudio.

@@

The workflow is controlled with the help of the main bash utility [`landcon.sh`](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/landcon.sh) in the top directory. This utility is used to run all the steps in the thesis analysis. Help can be acessed with `landcon.sh -h`

@@

  - `-r` Reclassify all STSIM outputs into Circuitscape inputs (resistance maps)
  - `-c` Run Circuitscape ([Julia package](https://github.com/Circuitscape/Circuitscape.jl))
  - `-d` Post process Circuitscape outputs into tabular data 
  - `-g` Make figures, knitting the Rmd document that is the base of the github page for this repo (link at the top).

@@

Finally you can also do:
  - `-a` Run ALL steps (again, provided data is provided)

@@

<!-- #### Docker image detailed breakdwon -->

>>>>

This repository contains all the code and some of the data that is needed to reproduce the work of my M.Sc. Thesis titled:

@@

```{}
docker run -it -e DISABLE_AUTH=true vlucet/land_con_monteregie:3.6.2-1 \
  /bin/bash && cd ~/land_con_monteregie
```

  - **Run docker image with Rstudio in your browser** (see [this post](https://ropenscilabs.github.io/r-docker-tutorial/02-Launching-Docker.html) for another example). Here you run the container in a detached mode (`-d`) on a local port (`-p 8787:8787`). Then, go to `http://192.168.99.100:8787` in your browser to access Rstudio.

@@

The workflow is controlled with the help of the main bash utility [`landcon.sh`](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/landcon.sh) in the top directory. This utility is used to run all the steps in the thesis analysis. Help can be accessed with `landcon.sh -h`

@@

  - `-a` Run ALL steps (again, provided data is provided)
  - `-r` Reclassify all STSIM outputs into Circuitscape inputs (resistance maps)
  - `-c` Run Circuitscape ([Julia package](https://github.com/Circuitscape/Circuitscape.jl))
  - `-d` Post process Circuitscape outputs into tabular data 
  - `-g` Make figures, knitting the Rmd document that is the base of the GitHub page for this repo (link at the top). **This is the only fully reproducible step.** in the absence of additional data.

@@

@@

<!-- #### Docker image detailed breakdown -->

### 2020-08-21 docs/msc_thesis_figures.Rmd
update many

**This regroups most of the figures in the thesis (appendix figures are not included, except for the ROC resample figures and BAU simulated land use change).**

@@

@@

ROC curves from fitting both models, plotted with the `patchwork` package.

@@

##### Other code for calculation

Compute auc / precision on predictions.

```{r eval=FALSE, include=FALSE}

>>>>

**This regroups most of the figures in the thesis (appendix figures are not included, except for the ROC resample figures, the BAU simulated land use change and the radar graph for change in flow for both chapters).**

@@

Change in mean flow (in \% of the the 2010 flow) between 2010 (observed) and 2100 (predicted), contrasting BAU scenario (solid line) with all other scenarios from borth chapters - radar graph.

@@

ROC curves from fitting both models (with resampling), plotted with the `patchwork` package.

@@

```{r eval=FALSE, include=FALSE}
##### ##### ##### ##### ##### ##### ##### 
#####  Other code for calculation   ##### 
##### ##### ##### ##### ##### ##### #####

# Compute auc / precision on predictions.
